---
title: "CourserProject1"
author: "Li Jiaan"
date: '2022-07-18'
output: html_document
---
##Assignment Instructions
1. Code for reading in the dataset and/or processing the data
2. Histogram of the total number of steps taken each day
3. Mean and median number of steps taken each day
4. Time series plot of the average number of steps taken
5. The 5-minute interval that, on average, contains the maximum number of steps
6. Code to describe and show a strategy for imputing missing data
7. Histogram of the total number of steps taken each day after missing values are imputed
8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
9. All of the R code needed to reproduce the results (numbers, plots, etc.) in the report

```{r, echo=TRUE}
library("ggplot2")
```

##Step 1
```{r, echo=TRUE}
setwd("~/Downloads")
data <- read.csv("activity.csv")
```

##Step 2 
```{r, echo=TRUE}
stepsPerDate <- aggregate(steps~date, data, sum, na.rm=TRUE) 
##To sum all steps in "data" and make a new data frame
##aggregate() splits a dataframe into subsets
hist(stepsPerDate$steps, xlab="Daily Steps", ylab="Frequency/Days")
```

##Step 3
```{r, echo=TRUE}
meansteps <- mean(stepsPerDate$steps)
meansteps
mediansteps <- median(stepsPerDate$steps)
mediansteps
```

##Step 4
```{r, echo=TRUE}
library(ggplot2)
datainterval <- aggregate(steps~interval, data, mean)
View(datainterval)
timeseries <- ggplot(datainterval,aes(interval,steps))
timeseries + geom_line()
```

##Step 5
```{r, echo=TRUE}
totalNA <- sum(is.na(data$steps))
##Show total number of NA values in "steps" column of "data" dataframe
```
##Step 6 and 7
```{r, echo=TRUE}
data[is.na(data)] = 0
datanoNA <- data
##Denote NA values as "0" and create a new dataset
stepsPerDatenoNA <- aggregate(steps~date, datanoNA, sum)
hist(stepsPerDatenoNA$steps, xlab="Daily Steps", ylab="Frequency/Days")
meanstepsnoNA <- mean(stepsPerDatenoNA$steps)
medianstepsnoNA <- median(stepsPerDatenoNA$steps)
##Replace the previous steps for the dataset without NA values
```

##Step 8
```{r, echo=TRUE}
dataYesNA <- read.csv("activity.csv") ##Beacuse original "data" data frame was 
##overwritten by data[is.na(data)] = 0
dataYesNA$day <- strptime(dataYesNA[,2], "%Y-%m-%d")
dataYesNA$weekdays <- weekdays(dataYesNA$day)
df1 = subset(dataYesNA,dataYesNA$weekdays == "星期六" |
               dataYesNA$weekdays == "星期天")
df2 = subset(dataYesNA,dataYesNA$weekdays != "星期六" &
               dataYesNA$weekdays != "星期天")
##Make new columns. "day" converts the "date" into the data type 
##that can be read by weekdays() function.
##For some reason the weekdays are shown in Chinese.

df1mean <- aggregate(steps~interval, df1, mean)
View(df1mean)
df2mean <- aggregate(steps~interval, df2, mean)
View(df2mean)

par(mfrow = c(1, 2))
with(df1mean,plot(interval,steps, type="l", xlab="Interval - Weekend"))
with(df2mean,plot(interval,steps, type="l", xlab="Interval - Weekend"))
```

##Step 9
```{r, echo=TRUE}
setwd("~/Downloads")
data <- read.csv("activity.csv")
View(data)
stepsPerDate <- aggregate(steps~date, data, sum, na.rm=TRUE) 
##To sum all steps in "data" and make a new data frame
##aggregate() splits a dataframe into subsets
hist(stepsPerDate$steps, xlab="Daily Steps", ylab="Frequency/Days")

"Calculate and report the mean and median of the total number of steps taken per day
"
meansteps <- mean(stepsPerDate$steps)
mediansteps <- median(stepsPerDate$steps)

datainterval <- aggregate(steps~interval, data, mean)
View(datainterval)
timeseries <- ggplot(datainterval,aes(interval,steps))
timeseries + geom_line()

maxinterval <- datainterval[which.max(datainterval$steps),]$interval
##use which.max() to find the max steps and the corresponding interval

totalNA <- sum(is.na(data$steps))
##Show total number of NA values in "steps" column of "data" dataframe

data[is.na(data)] = 0
datanoNA <- data
stepsPerDatenoNA <- aggregate(steps~date, datanoNA, sum)
hist(stepsPerDatenoNA$steps, xlab="Daily Steps", ylab="Frequency/Days")
meanstepsnoNA <- mean(stepsPerDatenoNA$steps)
medianstepsnoNA <- median(stepsPerDatenoNA$steps)
##Replace the previous steps for the dataset without NA values

dataYesNA <- read.csv("activity.csv") ##Beacuse original "data" data frame was 
##overwritten by data[is.na(data)] = 0
dataYesNA$day <- strptime(dataYesNA[,2], "%Y-%m-%d")
dataYesNA$weekdays <- weekdays(dataYesNA$day)
df1 = subset(dataYesNA,dataYesNA$weekdays == "星期六" |
               dataYesNA$weekdays == "星期天")
df2 = subset(dataYesNA,dataYesNA$weekdays != "星期六" &
               dataYesNA$weekdays != "星期天")
##Make new columns. "day" converts the "date" into the data type 
##that can be read by weekdays() function.
##For some reason the weekdays are shown in Chinese.

df1mean <- aggregate(steps~interval, df1, mean)
View(df1mean)
df2mean <- aggregate(steps~interval, df2, mean)
View(df2mean)

par(mfrow = c(1, 2))
with(df1mean,plot(interval,steps, type="l", xlab="Interval - Weekend"))
with(df2mean,plot(interval,steps, type="l", xlab="Interval - Weekend"))
```